Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-04-06 docs/ms.tex
Update ms.tex
update me.tex

While making the posterior samples $p(g,\alpha|Data)$ we choose to
use the classical Gibbs sampler.

@@

While the conditional distribution of one variable given all others
is just proportional to the joint distribution

\begin{equation}
p(x_{j}|x_{1},....,x_{j-1},x_{j+1}...,x_{n})\varpropto p(x_{1},.....,x_{n})
\end{equation}

>>>>

While making the posterior samples $p(\vec{g},\alpha|Data)$ we choose to
use the classical Gibbs sampler.

@@

The conditional probability distribution of one variable given all the other variables are proportional to their joint probability distribution

\begin{equation}
p(x_{j}|x_{1},....,x_{j-1},x_{j+1}...,x_{n})\propto p(x_{1},.....,x_{n})
\end{equation}
